\backmatter
\mygeometry
\fancypagestyle{plain}{
    \fancyhf{}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}
    \fancyfoot[RO]{\makebox[\paperwidth][r]{\hspace*{\oddsidemargin}\thepage\hspace{\dimexpr\marginparwidth+1.75\marginparsep-0.25in\relax}}}
}
\RaggedRight

\mygeometry
\chapter{Declaration of independence}
\justifying
I hereby declare that I have written this dissertation independently, using only the aids and resources indicated. I have not applied for a doctoral degree elsewhere and do not hold a corresponding doctoral degree. I declare that I have not already submitted the dissertation or parts thereof to another scientific institution and that it has neither been accepted nor rejected there. I declare that I am aware of the doctoral regulations of the Faculty of Life Sciences of Humboldt University of Berlin dated March 5, 2015, on which the procedure is based. Furthermore, I declare that no cooperation with commercial doctoral advisors has taken place and that the principles of the Humboldt University of Berlin for ensuring good scientific practice have been observed.

\begin{center}
{\Large \textbf{Selbstständigkeitserklärung}}
\end{center}

\noindent \textit{Hiermit erkläre ich, die Dissertation selbstständig und nur unter Verwendung der angegebenen Hilfen und Hilfsmittel angefertigt zu haben. Ich habe mich anderwärts nicht um einen Doktorgrad beworben und besitze keinen entsprechenden Doktorgrad. Ich erkläre, dass ich die Dissertation oder Teile davon nicht bereits bei einer anderen wissenschaftlichen Einrichtung eingereicht habe und dass sie dort weder angenommen noch abgelehnt wurde. Ich erkläre die Kenntnisnahme der dem Verfahren zugrunde liegenden Promotionsordnung der Lebenswissenschaftlichen Fakultät der Humboldt-Universität zu Berlin vom 5. März 2015. Weiterhin erkläre ich, dass keine Zusammenarbeit mit gewerblichen Promotionsberaterinnen / Promotionsberatern stattgefunden hat und dass die Grundsätze der Humboldt-Universität zu Berlin zur Sicherung guter wissenschaftlicher Praxis eingehalten wurden.}

\vspace{0.5cm}
\flushright{
Berlin,  \rule{5cm}{0.4pt}  2023
\vspace{1.0cm}
\\
Rafael Deliz-Aguirre
}

\ifodd\value{page}
\hbox{}
\newpage
\fi

\thispagestyle{empty} % No headers or footers for this page
\vspace*{\fill} % This pushes the content after it to the bottom
\begin{center}
\begin{adjustwidth}{1in}{1in}

{\Large \textbf{Colophon}}

\vspace{1cm}

This thesis, titled \textit{\thesistitle}, was typeset using the \LaTeX\ document preparation system, created by Leslie Lamport ({\url{https://www.latex-project.org/}}), and based on Donald Knuth's \TeX. It is made with the \texttt{classicthesis} template by André Miede ({\url{https://bitbucket.org/amiede/classicthesis/}}).

\vspace{0.5cm}

The bibliography was managed by Bibtex using the Vancouver reference style. Diagrams and illustrations were crafted using the \texttt{graphicx} package, Adobe Illustrator, Microsoft PowerPoint and BioRender ({\url{https://www.biorender.com/}}).

\vspace{0.5cm}

The main body of the text is set in 10pt using the font \TeX\ \texttt{Gyre Pagella}. The margin text is set to 8pt. Monospaced text uses \texttt{DejaVu Sans}. Margins are set to 1.25" (3.2 cm) inside, 2.75" (7.0 cm) outside, 1" (2.5 cm) top and bottom. Margin text is 1.75" (4.4 cm) wide and is spaced 0.25" (0.6 cm) from the main body.

\vspace{0.5cm}

This book was compiled using Xe\LaTeX\ on Overleaf, and used several packages from the Comprehensive \TeX\ Archive Network (CTAN).

\vspace{0.5cm}

Compilation date: \today. % Consummatum est. Deo gratias.
\end{adjustwidth}
\end{center}
